The Name of the Title is Hope

### 2022-09-07 input/2_introduction.tex
Update 2_introduction.tex

The sense of agency refers to the experience of being in control of our own voluntary actions, instead of them feeling as though they randomly happen to us. This being in the "driving seat when it comes to our own actions"~\cite{Moore2016-ubd} can be subdivided into the \textit{feeling} of agency, a low level pre-reflective sensory process, and a more higher level reflective cognitive process, the \textit{judgement} of agency~\cite{Moore2016-ub, Danry2022-xk}.

When integrating with computers, the key design goal is to maintain this pre-reflective experience of agency. With hardware that allows physically moving a user's body becoming increasingly lightweight and seamless. Wearable exoskeletons move a user's body by applying forces to the extremities, for example by pulling on the fingertips (see Dexmo Haptic Glove \footnote{https://www.dextarobotics.com/}) while electrical muscle stimulation (EMS) makes the user's extremities move by sending current into the muscle activating nerves.

>>>>

Technological advances in hardware that allow physically moving a user's body have reignited the dreams of overcoming human limitations, recorvering lost abilities as well as simplifying skill acquisition. Wearable exoskeletons move a user's body by applying forces to the extremities, for example by pulling on the fingertips (see Dexmo Haptic Glove \footnote{https://www.dextarobotics.com/}) while electrical muscle stimulation (EMS) makes the user's extremities move by sending current into the muscle activating nerves. These technologies are becoming increasingly seamless to use. However, augmented user's frequently report dissociative experiences following augmented action. They do not experience agency.

The sense of agency refers to the experience of being in control of our own voluntary actions, instead of them feeling as though they randomly happen to us. This being in the "driving seat when it comes to our own actions"~\cite{Moore2016-ubd} can be subdivided into the \textit{feeling} of agency, a low level pre-reflective sensory process, and a more higher level reflective cognitive process, the \textit{judgement} of agency~\cite{Moore2016-ub, Danry2022-xk}. The key challenge in human \textit{physical augmentation} is to create an experience of pre-reflective agency, so user's feel as though they are in the "driving seat" once again.

% What have others done to address this and what do we propose "instead"
